A holomorphic approach to membranes and fivebranes

### 2022-06-16 fivebranes/index.tex
cleaned up

We now compute the equivariant character counting local operators of the holomorphic twist of the theory on a large number of fivebranes. 
Unlike the analysis above, we will the twisted holography proposal to compute this character.

Let us briefly recall the proposal specialized to our situation \surya{more elaboration elsewhere}. Let $\cL$ denote the local $L_{\infty}$ algebra underlying the minimal twist of 11 dimensional supergravity on $\R_{t}\times \C^{3}_{z_{i}}\times \C^{2}_{w_{a}}$. Consider a stack of $N$ fivebranes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\pi : \R\times \C^{5}\to \C^{3}_{z_{i}}$ denote the canonical projection. The pushforward $\pi_{*} C^{*}(\cL)$ has the structure of a factorization algebra on $\C^{3}$

The twisted holography proposal asserts that the factorization algebra of local observables $\Obs_{M5}$ of the minimally twisted M5 brane theory in the large $N$ limit is a deformation of the Koszul dual $(\pi_{*} C^{\bullet}(\cL))^{!}$.

Since quantities like indices are deformation invariant, we need not consider such deformations for now. In fact in this section we may, and will, replace the local Lie algebra $\cL$ with the abelian local dg Lie algebra which underlies the free limit of the twisted supergravity theory.
Explicitly, $\cL$ is given by the following sheaf of $\Z/2$-graded cochain complexes
\[
\begin{tikzcd}
  &  \ul{\rm even} & \ul{\rm odd} \\
 \mu \in & \Omega^{\bullet}_{\R}\otimes\PV^{1,\bullet}_{\C^{5}} \ar[r, "\del_{\Omega}"] & \Omega^{\bullet}_{\R}\otimes\PV^{0,\bullet}_{\C^{5}}\\
 \gamma \in & \Omega^{\bullet}_{\R}\otimes\Omega^{0,\bullet}_{\C^{5}} \ar[r, "\del"]
& \Omega^{\bullet}_{\R}\otimes\Omega^{1,\bullet}_{\C^{5}}\end{tikzcd}
.\]

%Let us describe the restriction $\iota^* \cL$ along the inclusion of the brane.
%The $\mu$-field decomposes into vector field components which point along and transverse to the brane
%\[
%\mu
%\]
%
%is the sheaf of $\Z/2$-graded cochain complexes
%\[
%\begin{tikzcd}
%  &  \ul{\rm even} & \ul{\rm odd} \\
% \mu|_{w=t=0} \in & \PV^{1,\bullet}_{\C^{3}} \ar[r, "\del_{\Omega}"] & \PV^{0,\bullet}_{\C^{3}}\\
% \gamma|_{w=t=0} \in & \Omega^{0,\bullet}_{\C^{3}} \ar[r, "\del"]
%& \Omega^{1,\bullet}_{\C^{3}}\end{tikzcd}
%.\]

We wish to count local operators, which are given by the costalk at $0\in \C^{3}$ of $\Obs_{M5}$. Let us first describe $\Obs_{M5}$ more explicitly. By the Poincare and $\dbar$ Poincare lemmas, we have quasi-isomorphisms for each $U\subset \C^{3}$ open
\[
\Obs_{M5}(U) = \Sym \left( \begin{tikzcd}  \end{tikzcd} \right)
\]

The local observables are given by $\lim _{U\ni 0} \Obs_{M5}(U)$.

We first introduce the following notation for representatives of classes in compactly supported Dolbeault cohomology. We write $\delta^{(a,b,c)}$ to denote the derivative of the delta function $\del_{z_{1}}^{a}\del_{z_{2}}^{b}\del_{z_{3}}^{c}\delta_{t=w_{a}=0}$.

\begin{lem}
  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}\left ( \Obs_{M5}(0)\right )=\Sym (\Pi V_{\gamma}\oplus  V_{\mu})\] where
  \begin{itemize}
    \item $V_{\gamma}$ is spanned by
          \begin{align}
            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}dz_{1} \\
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{2}, \ \ \
             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{3} \\
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{1}, \ \ \
            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{2}
          \end{align}

          where $a, b, c, k, l \geq 0$.
    \item $V_{\mu}$ is spanned by
          \begin{align}
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(a-1,b, c)}w_{1}^{k-1}w_{2}^{l}\del_{z_{1}},\
             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_2}-l\delta^{(a-1,b, c)}w_{1}^{k-1}w_{2}^{l-1}\del_{z_{1}}\text{ where }a > 0, b,c,k,l \geq 0 \\
            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(0,b-1,c)}w_{1}^{k-1}w_{2}^{l}\del_{z_{2}}, \ \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}\del_{w_2}-l\delta^{(0,b-1,c)}w_{1}^{k}w_{2}^{l-1}\del_{z_{2}}\text{ where }b > 0,c,k,l \geq 0 \\
            & \delta^{(0,0,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-k\delta^{(0,0,c-1)}w_{1}^{k-1}w_{2}^{l}\del_{z_{3}}, \ \delta^{(0,0,c)}w_{1}^{k}w_{2}^{l}\del_{w_1}-l\delta^{(0,0,c-1)}w_{1}^{k}w_{2}^{l-1}\del_{z_{3}}\text{ where } c > 0,k,l \geq 0 \\
            & \delta^{(0,0,0)}w_{2}^{l}\del_{w_1}, \ \delta^{(0,0,0)}w_{1}^{k}\del_{w_2}\text{ where }k,l \geq 0
          \end{align}
  \end{itemize}
\end{lem}
\begin{proof}
  We compute cohomology using a spectral sequence associated to a two-step filtration by polyvector field and holomorphic form degree. The $E_{1}$ page is the $d+\dbar$ cohomology and is given by the symmetric algebra on

  \[
\begin{tikzcd}
\ul{\rm even} & \ul{\rm odd} \\
H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \iota^{*}T_{\C^{5}})) \ar[r, "\del_{\Omega}"] & H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO) )\\
H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3},  \iota^{*}T^{*}_{\C^{5}}))& H^{\bullet}(\Omega^{0,\bullet}_{c} (\C^{3}, \cO)) \ar[l, "\del"]
\end{tikzcd}
.\]

\surya{...}

\end{proof}

We consider the equivariant character of local operators of the holomorphic twist of a large number of fivebranes with respect to a finite dimensional subalgebra 
\[
\lie{sl}(3)\times \lie{sl}(2)\times \lie {gl}(1)\subset E(5|10)
\]
which embeds in the following way:
\begin{itemize}
\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect_0(\Hat{D}^3) \subset \Vect_0 (\Hat{D}^5)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
where $(a_{ij}) \in \lie{sl}(3)$. 
\item The Lie algebra $\lie{sl}(2)$ rotates the directions $\C_{w_1} \times \C_{w_2}$ transverse to the brane.
\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by the vector field 
\beqn\label{vf1}
\sum_i z_i \frac{\del}{\del z_i} - \frac23 \sum_{j} w_j \frac{\del}{\del w_j} \in \Vect_0(\Hat{D}^5).
\eeqn
\end{itemize}

>>>>

We now compute the equivariant character counting local operators of the holomorphic twist of the theory on a large number of fivebranes. 
Unlike the analysis above, we will the twisted holography proposal to compute this character. We consider the equivariant character of local operators of the holomorphic twist of a large number of fivebranes with respect to a finite dimensional subalgebra
\[
\lie{sl}(3)\times \lie{sl}(2)\times \lie {gl}(1)\subset E(5|10)
\]
which embeds in the following way:
\begin{itemize}
\item The Lie algebra $\lie{sl}(3)$ is a subalgebra of $\Vect_0(\Hat{D}^3) \subset \Vect_0 (\Hat{D}^5)$ consisting of linear coefficient vector fields $\sum_{i,j} a_{ij} z_i \frac{\del}{\del z_j}.$
where $(a_{ij}) \in \lie{sl}(3)$. 
\item The Lie algebra $\lie{sl}(2)$ rotates the directions $\C_{w_1} \times \C_{w_2}$ transverse to the brane.
\item The one-dimensional Lie algebra $\lie{gl}(1)$ is spanned by the vector field 
\beqn\label{vf1}
\sum_i z_i \frac{\del}{\del z_i} - \frac23 \sum_{j} w_j \frac{\del}{\del w_j} \in \Vect_0(\Hat{D}^5).
\eeqn
\end{itemize}
